---
title: Week 3
subtitle: Haoan Wang
author: 
  - Martin
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it.

The scatter plot will allow us to identify any noticeable trends or patterns in the issuance of marriage licenses. For instance, we might observe peaks during specific seasons, indicating breeding periods when penguin pairs are more likely to bond. Understanding when these licenses are issued can provide insights into penguin social structures and mating behaviors. This could lead to hypotheses about factors influencing bonding, such as environmental conditions or population dynamics. The initial visualization can be a springboard for deeper statistical analyses, such as investigating correlations with other variables (e.g., species differences, habitat conditions) or applying time series analysis to predict future trends.


And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point                                                                          

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References
@talia, @opendatatorotno

